Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-02 paper/ms.tex
update manuscript

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
  Jupiter-sized.  However, its transits are grazing: $b > 0.92$ at
  3$\sigma$.  From TESS photometry alone, the planetary size lies
  within 0.58--3.87 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Multi-color photometry requires eclipsing companions to have nearly
  identical color as TOI$\,$837, ruling out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios are limited
  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
  837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

The Gaia imaging, reduced to its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
orange circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The resolved stars
that were of immediate concern for our false positive analysis were as
follows.
\begin{itemize}
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
    proper motions and parallax of this star imply it is comoving with
    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
    it may not be bound.
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

The Gaia DR2 data for Star A seems poorly behaved.  While Star A has
$G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE\footnote{ See the Gaia DPAC technical note
GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
2020-06-22. } value is available.
% The astrometric reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number
% of good astrometric observations) seems rather poor, at $8.6$.
We suspect that the photometric failure to produce an $Rp$ magnitude,
as well as its poor astrometric fit, are likely due to blending with
\tn.

@@

While alternative approaches are available for simultaneously fitting
space and ground based photometry (in addition to radial velocimetry),
we opted for this approach because {\it i)} the radial velocitmetry on
its own did not show evidence for a planetary signal, and {\it ii)} we
expected that this approach would provide the best measurement of the
planetary ephemeris, which is key for follow-up efforts.  The
assumption of a constant radius across all bandpasses was tested by
independently fitting each ground-based transit while letting the
planetary radius float (Section~\ref{subsec:colorphot}). The transit
depths did not significantly change between different bandpasses.

>>>>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
  Jupiter-sized.  However, its transits are grazing: $b > 0.92$ at
  3$\sigma$.  From TESS photometry alone, the planetary size lies
  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Multi-color photometry requires eclipsing companions to have nearly
  identical color as TOI$\,$837, ruling out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios are limited
  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
  837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

The Gaia imaging, reduced to its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
orange circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The resolved stars
that were of immediate concern for our false positive analysis were as
follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
    proper motions and parallax of this star imply it is comoving with
    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
    it may not be bound.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

The Gaia DR2 data for Star A seems poorly behaved.  While Star A has
$G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE\footnote{ See the Gaia DPAC technical note
GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
2020-06-22. } value is available.  We suspect that the photometric
failure to produce an $Rp$ magnitude, as well as its poor astrometric
fit, are likely due to blending with \tn.

@@

While alternative approaches are available for simultaneously fitting
space and ground based photometry (in addition to radial velocimetry),
we opted for this approach because {\it i)} the radial velocimetry on
its own did not show evidence for a planetary signal, and {\it ii)} we
expected that this approach would provide the best measurement of the
planetary ephemeris, which is key for follow-up efforts.  The
assumption of a constant radius across all bandpasses was tested by
independently fitting each ground-based transit while letting the
planetary radius float (Section~\ref{subsec:colorphot}). The transit
depths did not significantly change between different bandpasses.
